---
title: "Descriptives II: Dominant Frames"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r,echo=FALSE,message=FALSE}
library(foreign)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(scales)
library(tidyr)
library(stringr)
library(reshape2)
library(knitr)
library(kableExtra)
library(stringr)
```


```{r,echo=FALSE,message=FALSE,warning=FALSE}
# Prepare dataframe
library(dplyr)

load("dfFull.Rdata")
df=dfFull
df= df %>% mutate_all(na_if,"")

# Fix date
df=df %>% 
  mutate(date2=as.Date(date,format = "%Y-%m-%d"),
         year=str_extract(date, "^.{4}"),
         year2=year,
         year2=as.numeric(recode(year2, `2014`="1",`2015`="1",`2016`="2",`2017`="2",`2018`="3",`2019`="3")),
         dim=as.character(domFrame),
         dim=as.factor(recode(domFrame,
                    `Socio-Economic`="Economic",
                    `Values`="Economic",
                    `Governance`="Politics",
                    `Power`="Politics")))

dfTone=df %>% select(id0,tone1,tone2,tone3) %>% 
  melt(id="id0") %>% 
  rename(Tone=value)

dfSub=df %>% select(id0,subFrame1,subFrame2,subFrame3) %>% 
  melt(id="id0") %>% 
  select(value) %>% 
  rename(Subframe=value)

dfActor=df %>% select(id0,actor1,actor2,actor3) %>% 
  melt(id="id0") %>% 
  select(value) %>% 
  rename(Actor=value)

dfMyth=df %>% select(id0,myth1,myth2,myth3) %>% 
  melt(id="id0") %>% 
  select(value) %>% 
  rename(Myth=value)


dfl=cbind(dfTone,dfSub,dfActor,dfMyth)
dfl=dfl %>% 
  arrange(id0)

dfw=df %>% 
  select(id0,country,NetPayer,level,Europ,site,sourceType,
         sourceFormat,sourceLevel,wordN,searchTerm,
         date,date2,year,year2,dim,domTone2,vis,vis2)

dfl=merge(dfl,dfw,by="id0",all.x = TRUE,sort = F)


dfl=dfl %>% 
  mutate(Tone=as.factor(Tone),
    Tone=recode_factor(Tone, `Negative` = "Negative", 
                       `Balanced` = "Neutral", 
                       `Factual` = "Neutral",
                       `Positive` = "Positive",
                       .ordered = TRUE),
                       id0=factor(id0))
dfl=droplevels(dfl)

```

This is an overview of the Frames, a core element in the framing analysis.


## Dominant frames

Here we can see quite clearly some of the problems with the Dominant Frames. The cell count is extremely low or absent in most Frames, except for the socio-economic frame. The problem is compounded by territorial level disaggregation.

```{r,fig.width=8,fig.height=8}
df %>%
  group_by(country,level,domFrame) %>%
  count() %>% 
  ggbarplot("domFrame", "n",
            fill="domFrame",
            color = "darkgrey", 
            legend="none",
            palette = "RdBu",
            facet.by = c("country","level"),
            ylab = "",
            label = TRUE, 
            ncol=4,
            x.text.angle = 55,
            xlab = "") +
  ylim(0,65) +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  ggtitle("Dominant frames * Coutry * Level")

```

# A two-dimensional solution

We can partially address the low Frame cell count issue, in terms of data and perhaps conceptually too, by combining Frames into an overarching dimension. Economics (socio-economics and values) vs Politics (governance and power).

Here we can see a three-level combination if our core variables. 

```{r,fig.width=8,fig.height=7.5}
df %>%
  group_by(country,level,dim) %>%
  count() %>% 
  ggbarplot("dim", "n",
            fill="dim",
            color = "darkgrey", 
            legend="none",
            palette = "RdBu",
            facet.by = c("country","level"),
            ylab = "",
            label = TRUE, 
            #ncol=8,
            x.text.angle = 45,
            xlab = "") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  ggtitle("Dominant Dimension * Coutry * Level")

```


# Summary

Sub-frame needs to be recoded to get a decent distribution. The re-conceptualiastion still fits since it describes the overall problematique nicely: the politics versus the economis of CP.
