---
title: "Mixed effects ordinal regression: Model 1"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



# Overview

Model 2 refers to ALL answer options in the Actor responsibility variable coded as an EU is mentioned dummy (i.e., EU + other is mentioned). As shown below:

```{r,eval=FALSE,echo=TRUE}

# An EU dummy
df=df %>% mutate(Actor2=recode_factor(actor1,
                                      `National`="Domestic",
                                      `Subnational`="Domestic",
                                      `National + Subnational`="Domestic",
                                      `EU + National`="European",
                                      `EU + National + Subnational`="European",
                                      `EU + Subnational`="European",
                                      `National + Other country`="European",
                                      `EU`="European",
                                      `Other country`="European",
                                      `EU + Other country`="European"))

```


```{r,echo=FALSE,message=FALSE}

library(dplyr)
library(ggplot2)
library(ggpubr)
library(scales)
library(tidyr)
library(reshape2)
library(knitr)
library(kableExtra)
library(stringr)
library(ordinal)
library(ggeffects)
library(broom)

```


```{r,echo=FALSE,message=FALSE,warning=FALSE}
# UPLOAD FIXED DATAFRAME (Manually FIXED missing DATES)
load("~/Dropbox/testGitHub/regio/FINAL/df.Rdata")
```


```{r}
m0 = clmm(Tone ~ 1 +
            (1|country) + (1|site),
          Hess = TRUE,
          data = df,
          threshold = "flexible")


m1 = clmm(Tone ~ 
            Net + 
            bad_thing17 +  
            selfrule + 
            equi17 +
            (1|country) + (1|site),
          Hess = TRUE,
          data = df,
          threshold = "flexible")

m2 = clmm(Tone ~ 
            Net + 
            bad_thing17 +  
            selfrule + 
            equi17 +
            words + 
            year2 + 
            vis2 + 
            sourceFormat + 
            (1|country) + (1|site),
          Hess = TRUE,
          data = df,
          threshold = "flexible")


m3 = clmm(Tone ~ 
            Net + 
            bad_thing17 +  
            selfrule + 
            equi17 +
            words + 
            year2 + 
            vis2 + 
            sourceFormat + 
            level + 
            (1|country) + (1|site),
          Hess = TRUE,
          data = df,
          threshold = "flexible")



m4 = clmm(Tone ~ 
            Net + 
            bad_thing17 +  
            selfrule + 
            equi17 +
            words + 
            year2 + 
            vis2 + 
            sourceFormat + 
            level + 
            Actor2 + 
            dim + 
            (1|country) + (1|site),
          Hess = TRUE,
          data = df,
          threshold = "flexible")

m5 = clmm(Tone ~ 
            Net + 
            bad_thing17 +  
            selfrule + 
            equi17 +
            words + 
            year2 + 
            vis2 + 
            sourceFormat + 
            level + 
            Actor2 + 
            dim + 
            level:Actor2 + 
            level:dim +
            (1|country) +  (1|site),
          Hess = TRUE,
          data = df,
          threshold = "flexible")

m6 = clmm(Tone ~  
            words + 
            year2 + 
            vis2 + 
            sourceFormat + 
            level + 
            Actor2 + 
            dim + 
            level:Actor2 + 
            level:dim +
            (1|country) +  (1|site),
          Hess = TRUE,
          data = df,
          threshold = "flexible")


library(purrr)
models <- list(m0 = m0, m1 = m1, m2 = m2, m3=m3,
               m4=m4,m5=m5)
sum2=purrr::map_df(models, broom::tidy, .id = "model")
sum1=purrr::map_df(models, broom::glance, .id = "model")

make_stars <- function(pval) {
  stars = ""
  if(pval <= 0.001)
    stars = "***"
  if(pval > 0.001 & pval <= 0.01)
    stars = "**"
  if(pval > 0.01 & pval <= 0.05)
    stars = "*"
  if(pval > 0.05 & pval <= 0.1)
     stars = "XY"
  stars
}


sum2=sum2 %>% 
  mutate(signif = sapply(p.value, function(x) make_stars(x)),
         estimate=round(estimate,3),
         std.error=round(std.error,3),
         est=paste(estimate,signif,sep=""),
         est=paste(est,std.error,sep=" ("),
         est=paste(est, ")",sep="")) 

sum2=sum2 %>% 
  select(model,est)

md0=data.frame(t(VarCorr(m0)))
md1=data.frame(t(VarCorr(m1)))
md2=data.frame(t(VarCorr(m2)))
md3=data.frame(t(VarCorr(m3)))
md4=data.frame(t(VarCorr(m4)))
md5=data.frame(t(VarCorr(m5)))


cVar=rbind(md0,md1,md2,md3,md4,md5)
cVar=data.frame(unlist(cVar))
mod=c(0,1,2,3,4,5,0,1,2,3,4,5)
cVar=cbind(mod,cVar)
cVar=cVar %>% 
  arrange(mod)
write.csv(cVar,"cVar.csv")

labs1=c("edf","logLik","AIC","BIC")
sum1=sapply(sum1[labs1],function(x)
  round(x,1))
write.csv(sum1,"RegressionSummaries.csv")
write.csv(sum2,"RegrssionOutput.csv")

```


# Regression summaries
```{r,echo=TRUE}
# Model Intercept only ()
summary(m0)

# Model 1 (Macro)
summary(m1)

# Model 2 (Macro + Article)
summary(m2)

# Model 3 (Macro + Article + Meso)
summary(m3)

# Model 4 (Macro + Article + Meso + Micro)
summary(m4)

# Model 5 (interaction)
summary(m5)

# Model 6 (without country)
summary(m6)

```

# Comparison of models
```{r,echo=TRUE}
# Compare All models
a1=anova(m0,m1,m2,m3,m4,m5)
a1
a1=data.frame(a1)
write.csv(a1,"anova.csv")

# Compare M4 to M5 without country
anova(m5,m6)
```

# Plots

## 3 plots per core variable
```{r,fig.width=9,fig.height=12}
# Level
p1=ggpredict(m5, c("level"),type = "fe")
p0=p1 %>% 
  mutate(x=recode(x,`1`="Regional\nnews",`2`="National\nnews"),
         response.level=recode_factor(response.level,
                                      `1`="Tone:Negative",
                                      `2`="Tone:Neutral",
                                      `3`="Tone:Positive")) %>% 
  ggplot(aes(x=x, y=predicted)) + 
  geom_point(size=3) +
  geom_errorbar(aes(ymin=predicted-std.error, 
                    ymax=predicted+std.error),
                size=0.5,width=.1) +
  facet_grid(~response.level) +
  theme_bw(base_size = 18) +
  xlab("") +
  ylab("Predicted probabilities") +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  ylim(0,0.8) +
  ggtitle("Level")

# Level
p1=ggpredict(m5, c("dim"),type = "fe")
p2=p1 %>% 
    mutate(x=recode(x,`1`="Socio\neconomic",`2`="Political\ninstitutional"),
           response.level=recode_factor(response.level,
                                        `1`="Tone:Negative",
                                        `2`="Tone:Neutral",
                                        `3`="Tone:Positive")) %>% 
    ggplot(aes(x=x, y=predicted)) + 
    geom_point(size=3) +
    geom_errorbar(aes(ymin=predicted-std.error, 
                      ymax=predicted+std.error),
                  size=0.5,width=.1) +
    facet_grid(~response.level) +
    theme_bw(base_size = 18) +
    xlab("") +
    ylab("Predicted probabilities") +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
    ylim(0,0.8) +
  ggtitle("Type of Frame")
  
  
# Level
p1=ggpredict(m5, c("Actor2"),type = "fe")
p3=p1 %>% 
  mutate(x=recode(x,`1`="Domestic",`2`="European"),
         response.level=recode_factor(response.level,
                                      `1`="Tone:Negative",
                                      `2`="Tone:Neutral",
                                      `3`="Tone:Positive")) %>% 
  ggplot(aes(x=x, y=predicted)) + 
  geom_point(size=3) +
  geom_errorbar(aes(ymin=predicted-std.error, 
                    ymax=predicted+std.error),
                size=0.5,width=.1) +
  facet_grid(~response.level) +
  theme_bw(base_size = 18) +
  xlab("") +
  ylab("Predicted probabilities") +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  ylim(0,0.8) +
  ggtitle("Actor responsibility")

ggarrange(p0,p2,p3,nrow=3)

```



## Interaction plot using SE
```{r,fig.width=9,fig.height=8,message=FALSE}
p1=ggpredict(m5, c("level","Actor2","dim"),type = "fe")
#p1=data.frame(p1)

p1 %>% 
  mutate(x=recode(x,`1`="Regional\nnews",`2`="National\nnews"),
         response.level=recode_factor(response.level,
           `1`="Tone:Negative",
           `2`="Tone:Neutral",
           `3`="Tone:Positive")) %>% 
  ggplot(aes(x=x, y=predicted, group=group, color=group)) + 
  geom_line(position=position_dodge(0.2)) +  
  geom_point(position=position_dodge(0.2),size=3)+
  geom_errorbar(aes(ymin=predicted-std.error, 
                            ymax=predicted+std.error),
                size=0.5,width=.1,color="grey10",
                position=position_dodge(0.2)) +
  labs(color = "    Actor") +
  facet_grid(facet~response.level) +
  theme_bw(base_size = 18) +
  theme(legend.position = "top") +
  xlab("") +
  ylab("Predicted probabilities") +
  theme(panel.grid.major.y = element_blank(),
      panel.grid.minor.y = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank()) 
# +  guides(color = FALSE) +

```


## Interaction plot using Confidence Intervals
```{r,fig.width=9,fig.height=8,message=FALSE}
p1=ggpredict(m5, c("level","Actor2","dim"),type = "fe")
#p1=data.frame(p1)

p1 %>% 
  mutate(x=recode(x,`1`="Regional\nnews",`2`="National\nnews"),
         response.level=recode_factor(response.level,
           `1`="Tone:Negative",
           `2`="Tone:Neutral",
           `3`="Tone:Positive")) %>% 
  ggplot(aes(x=x, y=predicted, group=group, color=group)) + 
  geom_line(position=position_dodge(0.2)) +  
  geom_point(position=position_dodge(0.2),size=3)+
  geom_errorbar(aes(ymin=conf.low, 
                            ymax=conf.high),
                size=0.5,width=.1,color="grey10",
                position=position_dodge(0.2)) +
  facet_grid(facet~response.level) +
  theme_bw(base_size = 18) +
  theme(legend.position = "top") +
  xlab("") +
  ylab("Predicted probabilities") +
  labs(color = "Actor   ") +
  theme(panel.grid.major.y = element_blank(),
      panel.grid.minor.y = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank())

```


# Annex

#### Plot the two territoriality Interactions

As can be seen there are some effects, but difficult to decipher. This is because the effects are being masked by SubFrame and Actor reponsibility jointly.

```{r,fig.width=15,fig.height=5.5,message=FALSE}
# 2way FRAME
p1=ggpredict(m5, c("dim","level"),type = "fe") 

pp1=p1 %>% 
  mutate(x=recode(x,`1`="ECO",`2`="POL"),
         response.level=recode_factor(response.level,
                                      `1`="Tone:Negative",
                                      `2`="Tone:Neutral",
                                      `3`="Tone:Positive")) %>% 
  ggplot(aes(x=x, y=predicted, group=group, color=group)) + 
  geom_point(position=position_dodge(0.1),size=3)+
  geom_errorbar(aes(ymin=predicted-std.error, 
                    ymax=predicted+std.error),
                size=0.5,width=.3,color="grey10",
                position=position_dodge(0.1)) +
  labs(color = "") +
  facet_grid(~response.level) +
  theme_bw(base_size = 18) +
  theme(legend.position = "top") +
  xlab("") +
  ylab("Predicted probabilities") +
  ylim(0,1) +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  ggtitle("Sub-Frame")


# 2way FRAME
p1=ggpredict(m5, c("Actor2","level"),type = "fe") 

pp2=p1 %>% 
  mutate(x=recode(x,`1`="Domestic",`2`="European"),
         response.level=recode_factor(response.level,
                                      `1`="Tone:Negative",
                                      `2`="Tone:Neutral",
                                      `3`="Tone:Positive")) %>% 
  ggplot(aes(x=x, y=predicted, group=group, color=group)) + 
  geom_point(position=position_dodge(0.1),size=3)+
  geom_errorbar(aes(ymin=predicted-std.error, 
                    ymax=predicted+std.error),
                size=0.5,width=.3,color="grey10",
                position=position_dodge(0.1)) +
  labs(color = "") +
  facet_grid(~response.level) +
  theme_bw(base_size = 18) +
  theme(legend.position = "top") +
  xlab("") +
  ylab("") +
  ylim(0,1) +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  ggtitle("Actor responsibility")


ggarrange(pp1,pp2)
```

In this last graph we can see the effects more clearly. How actor responsibility and sub frame are affected by territoriality.

## Interaction plot (SE's) with Regional/National same line
```{r,fig.width=7.5,fig.height=5.5,message=FALSE}
p1=ggpredict(m5, c("dim","level","Actor2"),type = "fe") 

p1 %>% 
  mutate(x=recode(x,`1`="ECO",`2`="POL"),
         response.level=recode_factor(response.level,
                                      `1`="Tone:Negative",
                                      `2`="Tone:Neutral",
                                      `3`="Tone:Positive")) %>% 
  ggplot(aes(x=x, y=predicted, group=group, color=group)) + 
  geom_point(position=position_dodge(0.1),size=3)+
  geom_errorbar(aes(ymin=predicted-std.error, 
                    ymax=predicted+std.error),
                size=0.5,width=.3,color="grey10",
                position=position_dodge(0.1)) +
  labs(color = "    Territoriality") +
  facet_grid(facet~response.level) +
  theme_bw(base_size = 18) +
  theme(legend.position = "top") +
  xlab("") +
  ylab("Predicted probabilities") +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) 

```


## TESTING REDUCED MODEL: Interaction plot (SE's) with Regional/National same line
```{r,fig.width=7.5,fig.height=5.5,message=FALSE}
p1=ggpredict(m5, c("dim","level","Actor2"),type = "fe") 

p1 %>% 
  mutate(x=recode(x,`1`="ECO",`2`="POL"),
         response.level=recode_factor(response.level,
                                      `1`="Tone:Negative",
                                      `2`="Tone:Neutral",
                                      `3`="Tone:Positive")) %>% 
  ggplot(aes(x=x, y=predicted, group=group, color=group)) + 
  geom_point(position=position_dodge(0.1),size=3)+
  geom_errorbar(aes(ymin=predicted-std.error, 
                    ymax=predicted+std.error),
                size=0.5,width=.3,color="grey10",
                position=position_dodge(0.1)) +
  labs(color = "    Territoriality") +
  facet_grid(facet~response.level) +
  theme_bw(base_size = 18) +
  theme(legend.position = "top") +
  xlab("") +
  ylab("Predicted probabilities") +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) 

```

