---
title: "Descriptives II: Dominant Frames"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r,echo=FALSE,message=FALSE}
library(foreign)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(scales)
library(tidyr)
library(stringr)
library(reshape2)
library(knitr)
library(kableExtra)
library(stringr)
```


```{r,echo=FALSE,message=FALSE,warning=FALSE}
# Prepare dataframe
library(dplyr)

load("dfFull.Rdata")
df=dfFull
df= df %>% mutate_all(na_if,"")

# Fix date
df=df %>% 
  mutate(date2=as.Date(date,format = "%Y-%m-%d"),
         year=str_extract(date, "^.{4}"),
         year2=year,
         year2=as.numeric(recode(year2, `2014`="1",`2015`="1",`2016`="2",`2017`="2",`2018`="3",`2019`="3")),
         dim=as.character(domFrame),
         dim=as.factor(recode(domFrame,
                    `Socio-Economic`="Economic",
                    `Values`="Economic",
                    `Governance`="Politics",
                    `Power`="Politics")))

dfTone=df %>% select(id0,tone1,tone2,tone3) %>% 
  melt(id="id0") %>% 
  rename(Tone=value)

dfSub=df %>% select(id0,subFrame1,subFrame2,subFrame3) %>% 
  melt(id="id0") %>% 
  select(value) %>% 
  rename(Subframe=value)

dfActor=df %>% select(id0,actor1,actor2,actor3) %>% 
  melt(id="id0") %>% 
  select(value) %>% 
  rename(Actor=value)

dfMyth=df %>% select(id0,myth1,myth2,myth3) %>% 
  melt(id="id0") %>% 
  select(value) %>% 
  rename(Myth=value)


dfl=cbind(dfTone,dfSub,dfActor,dfMyth)
dfl=dfl %>% 
  arrange(id0)

dfw=df %>% 
  select(id0,country,NetPayer,level,Europ,site,sourceType,
         sourceFormat,sourceLevel,wordN,searchTerm,
         date,date2,year,year2,dim,domTone2,vis,vis2)

dfl=merge(dfl,dfw,by="id0",all.x = TRUE,sort = F)


dfl=dfl %>% 
  mutate(Tone=as.factor(Tone),
    Tone=recode_factor(Tone, `Negative` = "Negative", 
                       `Balanced` = "Neutral", 
                       `Factual` = "Neutral",
                       `Positive` = "Positive",
                       .ordered = TRUE),
                       id0=factor(id0))
dfl=droplevels(dfl)

```

This is an overview of the two dependent variables, Tone and Europeanization.


## Tone

Here we can see a rather low cell count for some groups. But still ok for modeling I would think.

### Dependent Variable I: Dominant Tone
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.width=9,fig.height=8}
df %>%
  group_by(country,level,domTone2) %>%
  count() %>% 
  ggbarplot(x="level",y="n",
            color = "grey20", fill="domTone2",
            palette = "RdBu",
            xlab = "",
            ylab="Count",
            legend.title="",
            facet.by = "country",
            label = TRUE, 
            position = position_dodge(0.9),
            x.text.angle = 45) +
  ggtitle("Tone * Country * Level")


```


### Dependent Variable II: Europeanization

Generally the Europeanization variable has a better distribution across the groups.

```{r,echo=FALSE,message=FALSE,warning=FALSE}
df %>%
  group_by(country,Europ) %>%
  count() %>% 
  ggbarplot(x="country",y="n",
            color = "grey20", fill="Europ",
            palette = "RdBu",
            xlab = "",
            ylab="Count",
            label = TRUE, 
            position = position_dodge(0.9),
            x.text.angle = 45) +
  ggtitle("Country by Europeanization")


```


And it even is OK with further disaggregation at the territorial level.


```{r,fig.width=8,fig.height=8}
df %>%
  group_by(country,level,Europ) %>%
  count() %>% 
  ggbarplot("Europ", "n",
            fill="Europ",
            color = "darkgrey", 
            legend="none",
            palette = "RdBu",
            facet.by = c("country","level"),
            ylab = "",
            label = TRUE, 
            ncol=4,
            x.text.angle = 55,
            xlab = "") +
  ylim(0,65) +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  ggtitle("Europ * Coutry * Level")

```



# Summary

Both variables are OK for the analysis.